The {TestIdeals} package for \emph{Macaulay2}

### 2019-01-29 Fsing/TestIdealsPaper/TestIdeals.tex
Updated paper as referee suggested.  Also made a change to how frobeniusPowerHelper works in the case of Strategy=>Safe.  It should be much faster that way.

\medskip
{\small
\begin{MyVerbatim}
i1 : S = ZZ/5[x,y,z];
i2 : f = x^3 + y^3 + z^3;
i3 : u = f^(5-1);
i4 : frobeniusRoot( 1, ideal u )
o4 = ideal (z, y, x)
o4 : Ideal of R

i5 : S = ZZ/7[x,y,z];
i6 : f = x^3 + y^3 + z^3;
i7 : u = f^(7-1)
i8 : frobeniusRoot( 1, ideal u )
o8 = ideal 1
o8 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

The output of \texttt{testModule} is a list, consisting of three items:
\begin{enumerate}[(1)]
\item The test module itself, given as an ideal of $R$.
\item The canonical module that contains the test module, given as an ideal of $R$.
\item The element $u$ described above (not displayed above, since it takes a lot of space).
\end{enumerate}

@@

Again, consider the maps $T^e : \omega_{R^{1/p^e}} \to \omega_R$ we have considered throughout this section.  It is a theorem of Hartshorne-Speiser, Lyubeznik, and Gabber \cite{HartshorneSpeiserLocalCohomologyInCharacteristicP,LyubeznikFModulesApplicationsToLocalCohomology,Gabber.tStruc} that the descending images
\begin{equation}\label{eq: descending images}
\omega_R \supseteq T(\omega_{R^{1/p}}) \supseteq \dots \supseteq T^e(\omega_{R^{1/p^e}}) \supseteq T^{e+1}(\omega_{R^{1/p^{e+1}}}) \supseteq \cdots
\end{equation}
stabilize for $e \gg 0$.
The function \texttt{HSLGModule} computes the stable submodule in this chain, called the \emph{HSLG module}, and returns a list containing the following items:
\begin{enumerate}[(1)]
   \item The HSLG module;
   \item The canonical module;
   \item The element $u$ representing the map on the canonical module (see
   \autoref{subsec.DualToFrobeniusOnQuotientRings});
   \item The value of $e > 0$ at which the descending images in \eqref{eq: descending images} stabilize.  This is sometimes also called the HSLG-number of the canonical module as a Cartier module.
\end{enumerate}

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z];
i2 : f = y^2*z^3-x^5-2*z^5;
i3 : frobeniusPower( 1/11, ideal f )
o3 = ideal 1
o3 : Ideal of R
i4 : u = f^(121-1);
i5 : frobeniusPower( 1/121, ideal u )
             2        3
o6 = ideal (z , x*z, x )
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

>>>>

\medskip
{\small
\begin{MyVerbatim}
i1 : S = ZZ/5[x,y,z];
i2 : f = x^3 + y^3 + z^3;
i3 : u = f^(5-1);
i4 : frobeniusRoot( 1, ideal u )
o4 = ideal (z, y, x)
o4 : Ideal of S

i5 : S = ZZ/7[x,y,z];
i6 : f = x^3 + y^3 + z^3;
i7 : u = f^(7-1)
i8 : frobeniusRoot( 1, ideal u )
o8 = ideal 1
o8 : Ideal of S
\end{MyVerbatim}
}\medskip

@@

The output of \texttt{testModule} is a list, consisting of three items:
\begin{enumerate}[(1)]
\item The test module itself, given as an ideal of $R$.
\item The canonical module that contains the test module, given as an ideal of $R$.  (Note the representation of the canonical module as an ideal is not unique, it is only unique up to isomorphism, hence it is important to return this module as well).
\item The element $u$ described above (not displayed above, since it takes a lot of space).
\end{enumerate}

@@

Again, consider the maps $T^e : \omega_{R^{1/p^e}} \to \omega_R$ we have considered throughout this section.  It is a theorem of Hartshorne-Speiser, Lyubeznik, and Gabber \cite{HartshorneSpeiserLocalCohomologyInCharacteristicP,LyubeznikFModulesApplicationsToLocalCohomology,Gabber.tStruc} that the descending images
\begin{equation}\label{eq: descending images}
\omega_R \supseteq T(\omega_{R^{1/p}}) \supseteq \dots \supseteq T^e(\omega_{R^{1/p^e}}) \supseteq T^{e+1}(\omega_{R^{1/p^{e+1}}}) \supseteq \cdots
\end{equation}
stabilize for $e \gg 0$.
The function \texttt{HSLGModule} computes the stable submodule in this chain, called the \emph{HSLG module}, and returns a list containing the following items:
\begin{enumerate}[(1)]
   \item The HSLG module;
   \item The canonical module, embedded (non-uniquely) as an ideal;
   \item The element $u$ representing the map on the canonical module (see
   \autoref{subsec.DualToFrobeniusOnQuotientRings});
   \item The value of $e > 0$ at which the descending images in \eqref{eq: descending images} stabilize.  This is sometimes also called the HSLG-number of the canonical module as a Cartier module.
\end{enumerate}

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z];
i2 : f = y^2*z^3-x^5-2*z^5;
i3 : frobeniusPower( 10/11, ideal f )
o3 = ideal 1
o3 : Ideal of R
i5 : frobeniusPower( 120/121, ideal f )
             2        3
o6 = ideal (z , x*z, x )
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip
